%                                                                 aa.dem
% AA vers. 8.2, LaTeX class for Astronomy & Astrophysics
% demonstration file
%                                                       (c) EDP Sciences
%-----------------------------------------------------------------------
%
%\documentclass[referee]{aa} % for a referee version
%\documentclass[onecolumn]{aa} % for a paper on 1 column  
%\documentclass[longauth]{aa} % for the long lists of affiliations 
%\documentclass[rnote]{aa} % for the research notes
%\documentclass[letter]{aa} % for the letters 
%\documentclass[bibyear]{aa} % if the references are not structured 
% according to the author-year natbib style

%
\documentclass{aa}  
%
%

\usepackage{graphicx}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{txfonts}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{hyperref}
\pdfoutput=1
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{gensymb}
\usepackage{fancyhdr}
\usepackage{times}
\usepackage{ulem}
%\usepackage{caption}
\usepackage{subcaption} 
\usepackage{float} 
\usepackage{color}
\usepackage{booktabs}
\usepackage{lscape}
\usepackage{xspace}
 

\definecolor{purple}{RGB}{76, 0,153}
\newcommand{\ch}[1]{{\color{purple}{#1}}}
\newcommand{\bg}[1]{\textcolor{orange}{#1}}
\newcommand{\TT}[1]{{\color{red}{TT: #1}}}

\newcommand{\dd}{{\rm d}}
\newcommand{\br}[1]{\left( #1 \right)}
\newcommand{\bc}[1]{\left\{ #1 \right\}}
\newcommand{\eqa}[1]{\begin{align}   #1 \end{align}}

\newcommand{\bb}[1]{\left[ #1 \right]}
\newcommand{\vek}[1]{\mbox{\boldmath $#1$}}

\newcommand{\software}[1]{\texttt{#1}}
\newcommand{\tttp}{$3\times2$pt\xspace}
\newcommand{\LCDM}{$\Lambda$CDM\xspace}

\newcommand{\be}{\begin{equation}}  \newcommand{\ee}{\end{equation}}

\begin{document} 

   \title{KiDS-1000 Cosmology: Multi-probe weak gravitational lensing and spectroscopic galaxy clustering constraints}

   \author{Catherine Heymans \inst{1,2}\thanks{Catherine Heymans: heymans@roe.ac.uk} 
   \and Tilman Tr\"oster\inst{1}\thanks{Tilman Tr\"oster: ttr@roe.ac.uk} 
   \and Marika Asgari\inst{1} 
   \and Chris Blake\inst{3}
   \and Hendrik Hildebrandt\inst{2}
   \and Benjamin Joachimi\inst{4}
   \and Chieh-An Lin\inst{1}
   \and Ariel~G.~S\'anchez\inst{5}
   \and Jan Luca Van den Busch\inst{2}
   \and Angus~H.~Wright\inst{2}
   \and the KiDS Collaboration
          }
\institute{Institute for Astronomy, University of Edinburgh, Royal Observatory, Blackford Hill, Edinburgh, EH9 3HJ, UK 
   \and
   Ruhr-Universität Bochum, Astronomisches Institut, German Centre for Cosmological Lensing (GCCL), Universitätsstr. 150, 44801, Bochum, Germany
   \and 
   Centre for Astrophysics \& Supercomputing, Swinburne University of Technology, P.O. Box 218, Hawthorn, VIC 3122, Australia
   \and
   Department of Physics and Astronomy, University College London, Gower Street, London WC1E 6BT, UK
   \and
   Max-Planck-Institut f\"ur extraterrestrische Physik, Postfach 1312, Giessenbachstrasse 1, D-85741 Garching, Germany
   %Department of Astrophysical Sciences, Princeton University, 4 Ivy Lane, Princeton, NJ 08544, USA
     % \and
   %Department of Physics, University of Oxford, Denys Wilkinson Building, Keble Road, Oxford OX1 3RH, U.K.
    }
   % Leiden Observatory, Leiden University, Niels Bohrweg 2, 2333 CA Leiden, the Netherlands
 %  \date{Received September 15, 1996; accepted March 16, 1997}

% 5 {} token are mandatory
 
  \abstract{We present a joint cosmological analysis of weak gravitational lensing observations from the Kilo-Degree Survey (KiDS-1000), with redshift-space galaxy clustering observations from the Baryon Oscillation Spectroscopic Survey (BOSS), and galaxy-galaxy lensing observations from the overlap between KiDS-1000, BOSS and the spectroscopic 2-degree Field Lensing Survey (2dFLenS).  This combination of large-scale structure probes breaks the degeneracies between cosmological parameters for individual probes, resulting in a constraint on the structure growth parameter $S_8=\sigma_8 \sqrt{\Omega_{\rm m}/0.3} = 0.769^{+0.018}_{-0.015}$, that has the same precision as that reported by the full-sky cosmic microwave background observations from Planck.   The recovered $S_8$ amplitude is low, however, by $8.2 \pm 2.6 $\% relative to Planck.   This result builds from a series of KiDS-1000 analyses where we validate our methodology with variable depth mock galaxy surveys,  our lensing calibration with image simulations and null-tests, and our optical-to-near-infrared redshift calibration with multi-band mock catalogues and a spectroscopic-photometric clustering analysis.   The systematic uncertainties identified by these analyses are folded through as nuisance parameters in our cosmological analysis.  Inspecting the offset between the marginalised posterior distributions, we find that the $S_8$-difference with Planck is driven by a tension in the matter fluctuation amplitude parameter, $\sigma_8$.   
We determine the level of agreement between the CMB and large-scale structure constraints using the Bayes factor and the prior-insensitive suspiciousness statistic. \ch{This final sentence will need some work/thought once the Planck comparison chains are completed.}
  }

 \keywords{gravitational lensing: weak, methods: data analysis, methods: statistical, surveys, cosmology: observations}

   \titlerunning{KiDS-1000: 3x2pt}
   \authorrunning{Heymans, Tr\"oster \& the KiDS Collaboration et al.}
   \maketitle
%
%________________________________________________________________
\input{Section_Introduction}
\input{Section_Data}
\input{Section_Results}
\input{Section_Conclusions}

\begin{acknowledgements}
We are completely indebted to Eric Tittley at the IfA for going well beyond the call of duty to save the KiDS-1000 data products after an explosion in our server room destroyed the RAID.   We also thank
Mike Jarvis for his continuing enhancements, clear documentation and maintenance of the excellent {\sc TreeCorr} software package and our external blinder Matthias Bartelmann who revealed the key for which of the three catalogues analysed was the true unblinded catalogue at the end of the KiDS-1000 study.   We also wish to thank the Vera C. Rubin Observatory LSST-DESC Software Review Policy Committee (Camille Avestruz, Matt Becker, Celine Combet, Mike Jarvis, David Kirkby, Joe Zuntz with CH) for their Software Policy document which we followed, to the best of our abilities, during the KiDS-1000 project.   Following this policy the software used to carry out the various analyses presented in this paper will be made public on publication of this paper. 
The figures in this work were created with \software{matplotlib} \citep{Hunter2007} and \software{getdist} \citep{Lewis2019}, making use of the 
\software{numpy} \citep{Oliphant2006} and \software{scipy} \citep{Jones2001} software packages. \\

This project has received funding from the European Union's Horizon 2020 research and innovation programme: We acknowledge support from the European Research Council under grant agreement No.~647112 (CH, TT, MA, CL and BG) and No.~770935 (HHi, AHW, JLvdB and AD). TT also acknowledges support under the Marie Sk\l{}odowska-Curie grant agreement No.~797794. CH and FK acknowledges support from the Max Planck Society and the Alexander von Humboldt Foundation in the framework of the Max Planck-Humboldt Research Award endowed by the Federal Ministry of Education and Research. HHi is supported by a Heisenberg grant of the Deutsche Forschungsgemeinschaft (Hi 1495/5-1). AK acknowledges support from Vici grant 639.043.512, financed by the Netherlands Organisation for Scientific Research (NWO). KK acknowledges support by the Alexander von Humboldt Foundation.\\
%
The results in this paper are based on observations made with ESO Telescopes at the La Silla Paranal Observatory under programme IDs 177.A-3016, 177.A-3017, 177.A-3018 and 179.A-2004, and on data products produced by the KiDS consortium. The KiDS production team acknowledges support from: Deutsche Forschungsgemeinschaft, ERC, NOVA and NWO-M grants; Target; the University of Padova, and the University Federico II (Naples).  Data processing for VIKING has been contributed by the VISTA Data Flow System at CASU, Cambridge and WFAU, Edinburgh. 

The BOSS-related results in this paper have been made possible thanks to SDSS-III. Funding for SDSS-III has been provided by the Alfred P. Sloan Foundation, the Participating Institutions, the National Science Foundation, and the U.S. Department of Energy Office of Science.   SDSS-III is managed by the Astrophysical Research Consortium for the Participating Institutions of the SDSS-III Collaboration including the University of Arizona, the Brazilian Participation Group, Brookhaven National Laboratory, Carnegie Mellon University, University of Florida, the French Participation Group, the German Participation Group, Harvard University, the Instituto de Astrofisica de Canarias, the Michigan State/Notre Dame/JINA Participation Group, Johns Hopkins University, Lawrence Berkeley National Laboratory, Max Planck Institute for Astrophysics, Max Planck Institute for Extraterrestrial Physics, New Mexico State University, New York University, Ohio State University, Pennsylvania State University, University of Portsmouth, Princeton University, the Spanish Participation Group, University of Tokyo, University of Utah, Vanderbilt University, University of Virginia, University of Washington, and Yale University.\\

The 2dFLenS-related results are based on data acquired through the Australian Astronomical Observatory, under program A/2014B/008. It would not have been possible without the dedicated work of the staff of the AAO in the development and support of the 2dF-AAOmega system, and the running of the AAT.\\

{ {\it Author contributions:}  All authors contributed to the development and writing of this paper.  The authorship list is given in three groups:  the lead authors (CH \& TT) followed by two alphabetical groups.  The first alphabetical group includes those who are key contributors to both the scientific analysis and the data products.  The second group covers those who have either made a significant contribution to the data products, or to the scientific analysis.}
\end{acknowledgements}


\bibliographystyle{aa} % style aa.bst
\bibliography{references} % your references 

\input{Appendices}


%-------------------------------------------------------------------


\end{document}

